Efficiently Handling Guards in the low level design of RPython's tracing JIT

### 2012-07-24 talk/vmil2012/paper.tex
write something about SPUR

Although there are several publications about tracing jut-in-time compilers, to
our knowledge, there are none that describe the use and implementation of
guards in this context. With the following contributions we aim to shed some
light (to much?) on this topic.
The contributions of this paper are:
\begin{itemize}
 \item
\end{itemize}

@@

>>>>

Although there are several publications about tracing just-in-time compilers, to
our knowledge, there are none that describe the use and implementation of
guards in this context. With the following contributions we aim to shed some
light (to much?) on this topic.
The contributions of this paper are:
\begin{itemize}
 \item
\end{itemize}

@@

SPUR~\cite{bebenita_spur:_2010} is a tracing JIT compiler
for a C\# virtual machine.
It handles guards by always generating code for every one of them
that transfers control back to the unoptimized code.
Since the transfer code needs to reconstruct the stack frames
of the unoptimized code,
the transfer code is quite large.
